---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

```{r setoptions, echo = FALSE}
#opts_chunk$set(echo = TRUE)
```

## Loading and preprocessing the data

```{r loadData}
stepsData <- read.csv("activity.csv")
```

  
## What is mean total number of steps taken per day?

Calculate the total number of steps taken per day and make a histogram of the total number of steps taken each day.
```{r}
steps <- tapply(stepsData$steps, stepsData$date, sum, na.rm = TRUE)
hist(steps, main = "Total Number of Steps Taken Each Day")
```

Calculate and report the mean and median of the total number of steps taken per day.
```{r}
mean(steps)
median(steps)
```
  
## What is the average daily activity pattern?

Make a time series plot of the 5-minute interval and the average number of steps taken, averaged across all days.
```{r}
stepsByInterval <- tapply(stepsData$steps, stepsData$interval, mean, na.rm = TRUE)
plot(names(stepsByInterval), stepsByInterval, type = "l",
     xlab = "5-minute interval", ylab = "average steps",
     main = "average steps taken in 5-minute interval, averaged across all days")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
names(which.max(stepsByInterval))
```
  
## Imputing missing values


  
## Are there differences in activity patterns between weekdays and weekends?
